### 2019-12-13 report/02-methods.Rmd
Fix op cleaning

```{r}
com <- ungroup(community_analysis) %>%
  select(opcod, species, biomass) %>%
  spread(species, biomass) %>%
  left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
  mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
  select(-opcod) %>%
  group_by(station) %>%
  summarise_all(list(median))

com_mat <- as.matrix(com[, names(com) != "station"]) 
```

@@

nmds <- metaMDS(com_mat, k=3, trymax = 100)

stressplot(nmds)
plot(nmds)
ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="gray",air=0.01)
```

>>>>

```{r}
com <- ungroup(community_analysis) %>%
  select(opcod, species, biomass) %>%
  spread(species, biomass) %>%
  left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
  filter(!is.na(station)) %>%
  mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
  select(-opcod) %>%
  group_by(station) %>%
  summarise_all(list(median))

com_mat <- as.matrix(com[, names(com) != "station"])
rownames(com_mat)  <- com$station

order_st <- match(temporal_community_metrics$station, com$station) 
tps_com_met <- temporal_community_metrics[order(order_st),]

@@

nmds <- metaMDS(com_mat, k=3, trymax = 100)
stressplot(nmds)
plot(nmds)
mysave(nmds, dir = mypath("report"), overwrite = TRUE)

bluefunc <- colorRampPalette(c("lightyellow", "darkred"))
ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="gray",air=0.01)
orditorp(nmds, display="sites",
  col= bluefunc(5)[findInterval(tps_com_met$richness_avg, seq(2,6))],
  # cex = scale(tps_com_met$biomass_med, center = FALSE),
  air=0.01, pch = "+")
```

### 2019-12-13 report/05-stability.Rmd
Add sub station dataset without holes in monitoring
Fix op cleaning

1. Stability total vs div + habitat 
2. Stability by trophic group vs diversity:trophic group:habitat
   - Random effects: catchement & # sampling years
   - Include composition in the analyses as [@sandau_including_2014]
3. SEM:
   - Paths:
     - Total Stability
     - Stability at trophic level 2 & trophic level 3
     - Diversity at trophic level 2 & trophic level 3
     - Altitude or PCA coordinates 
   - Groups: habitat 
   - Replicate for productivity
4. Test for different datasets

@@

```{r}
biomass_sem <- temporal_community_metrics %>%
  select(station, biomass_stab, biomass_med, richness_med, pielou_med,
  beta_bin_c) %>%
  left_join(select(synchrony, station, synchrony, cv_sp), by = "station") %>%
  rename(sync = synchrony,
    piel = pielou_med,
    prod = biomass_med 
  )
habitat_sem <- habitat_pressure %>% 
  select(station, alt, width_river_mean) %>%
  rename(width = width_river_mean)
net_sem <- temporal_network_metrics %>%
  select(station, connectance_corrected_med, w_trph_lvl_avg_med) %>%
  rename(c_c = connectance_corrected_med,
    t_lvl = w_trph_lvl_avg_med)

dsem <- biomass_sem  %>%
  mutate(log_rich = log10(richness_med)) %>%
  left_join(net_sem, by = "station") %>%
  left_join(habitat_sem, by = "station") %>%
  left_join(st_basin, by = "station") %>%
  na.omit()

@@

```{r}
library(lavaan)
options(width = 100)

@@

```{r, fig.dim = c(10, 7), fig.cap = "Lavaan SEM"}
debug(ggsem)
ggsem(lav_mod)
```

@@

```{r, fig.cap = "The basic SEM"}
corsem <- psem(
  lme(log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data),
  lme(log_cv_sp ~ log_rich + piel + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data),
  lme(log_rich ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(piel ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(c_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lm(log_stab ~ log_cv_sp + log_sync, data = lav_data)
)
output <- summary(corsem, .progressBar = F)
output$coefficients %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
source(mypath("R", "plot_methods.R"))
ggpiecewisesem(output)
```

```{r, fig.cap = "Biomass"}
prod_sem <- psem(
  lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data),
  lme(log_rich ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(piel ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(c_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = lav_data)
)
sumup_prod <- summary(prod_sem, .progressBar = F)
sumup_prod$coefficients %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

>>>>

1. Stability total vs div + habitat 
2. Stability by trophic group vs diversity:trophic group:habitat
   - Random effects: catchement & # sampling years
   - Include composition in the analyses as [@sandau_including_2014]
3. SEM:
   - Paths:
     - Total Stability
     - Stability at trophic level 2 & trophic level 3
     - Diversity at trophic level 2 & trophic level 3
     - Altitude or PCA coordinates 
   - Groups: habitat 
   - Replicate for productivity
4. Test for different datasets
   - factorise calcultation of temporal metrics

@@

```{r}
biomass_sem <- temporal_community_metrics %>%
  select(station, biomass_stab, biomass_med, richness_med, pielou_med,
  beta_bin_c) %>%
  left_join(select(synchrony, station, synchrony, cv_sp), by = "station") %>%
  rename(sync = synchrony,
    piel = pielou_med,
    prod = biomass_med 
  )
habitat_sem <- habitat_pressure %>% 
  select(station, alt, width_river_mean) %>%
  rename(width = width_river_mean)
net_sem <- temporal_network_metrics %>%
  select(station, connectance_corrected_med, w_trph_lvl_avg_med) %>%
  rename(c_c = connectance_corrected_med,
    t_lvl = w_trph_lvl_avg_med)
composition_axis <- nmds$points %>%
  as_tibble %>%
  mutate(station = as.integer(dimnames(nmds$points)[[1]]))

dsem <- biomass_sem  %>%
  mutate(log_rich = log10(richness_med)) %>%
  left_join(net_sem, by = "station") %>%
  left_join(habitat_sem, by = "station") %>%
  left_join(st_basin, by = "station") %>%
  left_join(composition_axis, by = "station") %>%
  na.omit()

@@

```{r, eval = FALSE}
library(lavaan)
options(width = 100)

@@

```{r, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Lavaan SEM"}
ggsem(lav_mod)
```

### Piecewiese SEM

@@

#### Stability

```{r, fig.cap = "The basic SEM"}
  corsem <- psem(
    lme(log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data),
    lme(log_cv_sp ~ log_rich + piel + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data),
    lme(log_rich ~ alt + width, random = ~ 1 | basin, data = lav_data),
    lme(piel ~ alt + width, random = ~ 1 | basin, data = lav_data),
    lme(c_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
    lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = lav_data),
    lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
    lm(log_stab ~ log_cv_sp + log_sync, data = lav_data)
  )
output <- summary(corsem, .progressBar = F)
output$coefficients %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")

source(mypath("R", "plot_methods.R"))
ggpiecewisesem(output)
```

```{r}
compute_psem <- function(.data) {
  corsem <- psem(
    lme(log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = .data),
    lme(log_cv_sp ~ log_rich + piel + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = .data),
    lme(log_rich ~ alt + width, random = ~ 1 | basin, data = .data),
    lme(MDS2 ~ alt + width, random = ~ 1 | basin, data = .data),
    lme(piel ~ alt + width, random = ~ 1 | basin, data = .data),
    lme(c_c ~ alt + width, random = ~ 1 | basin, data = .data),
    lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = .data),
    lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = .data),
    lm(log_stab ~ log_cv_sp + log_sync, data = .data)
  )
  output <- summary(corsem, .progressBar = F)

  output
}
test <- compute_psem(lav_data)
ggpiecewisesem(test)
```

```{r sensitivity, eval = FALSE}
myload(op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))

# Compute stability, network metrics, etc with the new datasets

# Compute SEMs
map(list(), compute_psem)

# Plot

```{r}
lav_data %>%
  ggplot(aes(x = log_rich, y = MDS1)) +
  geom_point() +
  labs(x = "Log of species richness", y = "Axis of composition")

#### Productivity

```{r, fig.cap = "Biomass"}
prod_sem <- psem(
  lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = lav_data),
  lme(MDS2 ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(log_rich ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(piel ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(c_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = lav_data)
)
sumup_prod <- summary(prod_sem, .progressBar = F)
sumup_prod$coefficients %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

```{r}
ggpiecewisesem(sumup_prod)
```

```{r colin_prod}
car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = lav_data))
```
